### 2016-02-09 Docs/FAQ/faq.tex
add docs about the new backtracing stuff + a new general indexing command

>>>>

\item {\em How can I get more information about floating point exceptions?}

\boxlib\ can intercept floating point exceptions and provide a helpful
backtrace that shows you where they were generated.  Compile with {\tt
  TEST=t} \otherindex{GNUmakefile}{TEST=t} in your {\tt GNUmakefile} (this is also
activated in debug-mode, with {\tt NDEBUG= }).  The floating point
exceptions include NaNs, divide by zero, and overflow.  When one of
these is hit, the code will abort, and the backtrace information will
be output to a file {\tt Backtrace.N}, where {\tt N} is the processor
number.  BoxLib will also initialize \multifab s with signaliing NaNs
to help uncover any floating point issues.

Handling of seg faults and interruption by control-C are always
enabled, so you can get a backtrace from the code by interrupting its
execution on the commandline (this can be useful for investigating
deadlocks).

Behind the scenes, \boxlib\ implements this capability via the
Linux/Unix {\tt feenableexcept} function (this is in {\tt
  backtrace\_c.cpp} in \boxlib).

Note that due to issues with header files, this backtrace capability
is not supported with the PGI compilers.
